---
title: "AAPI Data State Election Profile"
params:
  state: "test"
output:
  html_document:
    theme: simplex
    toc: true
    
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(DT)
library(readxl)
library(tidyverse)
data_jurisdiction <- read_excel('~/Dropbox/AAPIData HQ/2017-AAPI Electeds/byjurisdiction_edit.xlsx')
sheetlist<-excel_sheets('~/Dropbox/AAPIData HQ/2017-AAPI Electeds/byjurisdiction_edit.xlsx')
congress <- read_excel('~/Dropbox/AAPIData HQ/2017-AAPI Electeds/byjurisdiction_edit.xlsx',sheet = 1)
county <- read_excel('~/Dropbox/AAPIData HQ/2017-AAPI Electeds/byjurisdiction_edit.xlsx',sheet = 2)
congress <- congress %>% filter(State == params$state)
county <- county %>% filter(State == params$state)
currentstate <- congress$State[1]
seats <- nrow(congress)
counties<- nrow(county)
```


## Elected Officials in <span style="color:red">`r currentstate`</span>
> Here is a list of the curent AAPI Elected Officials in the State of <span style="color:red">`r currentstate`</span>
> List will be here

## Congressional Districts
<span style="color:red">`r currentstate`</span> has **`r seats`** Congressional Districts where AAPIs are more than 3% of the district population
```{r, echo=FALSE, message=FALSE, warning=FALSE}

#counties <- read_excel('byjurisdiction_edit.xlsx',sheet = 2)

datatable(congress,extensions = "Buttons",rownames= FALSE, options = list(dom = 'Brtip',
    buttons = c('copy', 'csv', 'excel'))) %>% formatPercentage('AAPI Proportion', 2) %>%
  formatCurrency(c("Total Pop", "Asian Alone", "NHPI Alone", "AAPI"),currency = "", interval = 3, mark = ",", digits=0)
#format(round(as.numeric(1000.64), 1), nsmall=1, big.mark=",")  
```

## Counties
<span style="color:red">`r currentstate`</span> has **`r counties`** counties where AAPIs are more than 3% of the county population
```{r, echo=FALSE, message=FALSE, warning=FALSE}

#counties <- read_excel('byjurisdiction_edit.xlsx',sheet = 2)

datatable(county,extensions = "Buttons",rownames= FALSE, options = list(dom = 'Brtip',
    buttons = c('copy', 'csv', 'excel'))) %>% formatPercentage('AAPI Proportion', 2) %>%
  formatCurrency(c("Total Pop", "Asian Alone", "NHPI Alone", "AAPI"),currency = "", interval = 3, mark = ",", digits=0)
#format(round(as.numeric(1000.64), 1), nsmall=1, big.mark=",")  
```

## County Subdivision
> Data Here

## School Board Data
> Data Here
